\tb{Place of Residence and Political Attitudes in Democracies Worldwide }

### 2018-11-22 Final Paper/PaperJLin.tex
Added discussions of Level of Democracy and Electoral Formula

@@

>>>>

The data in Table \ref{table15} suggests that there is a difference between urban and rurual residents when it comes to spending, but this pattern is not as emphasized in self-placement ideology. The results of this model confirms the work from previous literature to show that urban residents are more open to government spending to help a neighbor than residents in a rural area of a country. Yet, the interesting difference lies in the breakdown of self-placement on the ideology spectrum. While there is not as much significance between urban and rural residents, there are differences with each of the residence types that can be analyzed further.

@@

\subsubsection{By Level of Democracy}

A model that considers the interaction of a country's level of democracy and place of residence on an individual's political attitudes was conducted and the results suggests that the effect of place is more pronounced at lower levels of democracy. However, this is an effect that works in theory and not in practice. Countries with lower levels of democracy might have greater levels of divide between the quality of life in cities than suburbs than rural towns. This observation was displayed numerous times in previous analyses of polities where countries with lower levels of democracy were experiencing a greater difference between place and political attitudes, as exhibited in Asia. Yet, limitations in political expression might mask this reality, which suggests that further exploration in the data is necessary.

Additionally, the regression suggests that countries with great levels of freedom, which includes the majority of the polities that are included in this study, do not have interactive effects with regard to level of democracy. In other words, this result suggests that having freedoms related to democracy are great, but there may be other factors that mitigates the differences between places of residence and political attitudes. When we looked at countries in each region, there are countries with similar level of democracy, but stark differences in the relationship of core variables.

\subsubsection{By Regime Age}

To understand the interaction between the age of a regime and place of residence on political ideology, I ran a regression to explore these effects.

\subsubsection{By Electoral Formula}

For this section, we consider Electoral formula. Since there are only 3 categories that any country can select, it makes direct comparison more straightforward. Unlike the previous two discussions, this variable is not continuous, thereby making interactions not as suitable.

\begin{table}[H]
	\centering
	\caption{\tb{Ideology In Each Electoral Formula}}
	\begin{tabulary}{\linewidth}{l c c c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Majoritarian}&\tb{Proportional} &\tb{Mixed} \\
		\hline
		Small Town&-.6640*** &.0608 &-.1600** \\
		&(.0766)&(.0435) &(.0727) \\
		Suburban&-.6389*** &-.1894***&-.1260  \\
		&(.1042) &(.0451) &(.1180) \\
		Urban&-.5781*** &-.0327 &.2655*** \\
		&(.0710) &(.0388) &(.0644) \\
		Constant& 5.8256*** &5.5408***&5.5562*** \\
		&(.0543) &(.0297) &(.0531) \\
		Countries&5&21&6 \\
		N&8,350&28,869 &10,602 \\
		$R^2$&0.0114&0.0011 &0.0052 \\
		\hline 
	\end{tabulary} 
\\ 
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table16}
\end{table}

Table \ref{table16} shows the relationship of place of residence in countries grouped by their electoral formula.
